An investigation of times that a lack in good physical security practices led to a cyber security issue

### 2024-02-12 Paper/Paper.tex
Update paper

For instance, Google's Cyber Security Culture is stringent on including
physical security, one example being how they handle their data centers \cite{GoogleData}.
Google made a video describing the security of their centers. To emphasize why
the culture of cyber-security is important,
Stephanie Wong (a Google employee) admitted she "could talk all day
about cloud security, (but)physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.

@@

\section{Google's Plasma Globe}
One of the best ways to test security is by testing, verifying, and self-auditing
how well the security system holds up. Google went about this by creating a
"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with trying to hack Google.
Though this task certainly includes doing software-based attacks, one of the successful
attacks was a physical attack.

\subsection{Google's Plan of Attack}
The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
Only five plasma globes were created with a malicious modification to them.
The Red Team added an internal chip that would emulate a USB keyboard when plugged
in to a computer. After approximately 5-10 minutes, the device would
quickly type out a command to download a larger payload from the internet \cite{GoogleGlobeBlog}.
In order to give the device to Google's employees, the Red Team disguised the
device as an anniversary gift from Google (based off of LinkedIn).

@@

\subsection{Attack Analysis}
Ultimately, this attack was a phishing attack. The Red Team was able to convince
Google's employees to plug in a USB device that was given to them. The Red Team
was able to gain access to Google's Glasses internal documentation by using the
employee's credentials.

@@

\subsection{Mitigation}
Google learned from this breach and created a software that would listen to extremely
fast keystrokes from USB devices and block them. This software was then installed
on all of Google's computers, and publicly released \cite{Google02}.

While a software solution is a good start, it is not a complete solution. A theoretical
slow USB device could still be used to bypass this software. A better solution would
be to train employees to be aware of the dangers of plugging in unauthorized devices.

>>>>

For instance, Google's Cyber Security Culture is stringent on including
physical security, one example being how they handle their data centers \cite{GoogleData}.
Google made a video describing the security of their centers. To emphasize why
the culture of cyber-security is important,
Stephanie Wong (a Google employee) admitted she "could talk all day
about cloud security, (but) physical security (at Google) is still pretty new to me" \cite{GoogleDataVideo}.

@@

\section{Google's Plasma Globe}
One of the best ways to test security is by testing, verifying, and self-auditing
how well the security system holds up. Google went about this by creating a
"Red Team" \cite{GoogleRedTeamBlog}, a team of white-hat hackers that were tasked with
trying to hack Google (a testament to their cyber-security culture).
Though this job includes software-based attacks,
one of the successful attacks was a physical attack.

\subsection{Google's Plan of Attack}
The Red Team designed a Plasma Globe that had a USB cable attached to it for power.
Only five plasma globes were created with a malicious modification to them.
The Red Team added an internal chip that would emulate a USB keyboard when plugged
in to a computer. After approximately 5-10 minutes, the device would
quickly type out a command to download a larger payload from the internet \cite{GoogleGlobeBlog}.
In order to give the device to Google's employees, the Red Team disguised the
device as an anniversary gift from Google (using LinkedIn to find anniversaries) \cite{GoogleGlobeVideo}.

@@

\subsection{Attack Analysis}
Ultimately, this attack was a phishing attack. The Red Team was able to convince
Google's employees to plug in a USB device that was given to them. The Red Team
was able to gain access to Google's Glasses internal documentation by using the
employee's credentials \cite{GoogleGlobeVideo}.

@@

\subsection{Mitigation and Response}
Google learned from this breach and created a software that would listen to extremely
fast keystrokes from USB devices and block them. This software was then installed
on Google's computers, and the software was publicly released \cite{GoogleUSB,GoogleRedTeamBlog}.

While a software solution is a good start, it is not a complete solution. A theoretically
slow USB device could still be used to bypass this software. Cybersecurity hinges
on a solid cyber secure culture, and humans are the core of that culture.

Whether a USB device is found in the parking lot or given as a gift, it is important
to ensure that employees are aware of the dangers of plugging in unauthorized devices.
Thankfully, the source of the attack was not a malicious actor, a testament to 
Google's cyber secure culture.

\section{Remote Hacking of Oldsmar's Water Treatment System}
An interesting idea of physical security is the idea of remote physical security.
The Oldsmar water treatment plant in Florida was hacked in February 2021. The
attacker was able to remotely access the system
"through a dormant software called TeamViewer" \cite{CCNFlorida}.
Unfortunately, not much is known about the attack, and Martina Dier (a spokeswoman
for TeamViewer) stated "Based on cooperative information sharing, a diligent technical
investigation did not find any indication for suspicious connection activity via our
platform" \cite{CCNFlorida}.

\section{Method of Attack}
It is believed that the attacker was able to remotely access the system through
TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
in the water from 100 parts per million to 11,100 parts per million.
